Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-27 paper/paper.tex
Adding fish image analysis references.

Since the digital collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible. Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
As a step towards improving metadata in specimen research image collections, members of the Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digital specimen.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.
In order to test and validate our methods, we applied them to a set of 7,247
images drawn from the Illinois Natural History Survey (INHS) Collection.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results are presented, followed by a discussion. The conclusion highlights key findings and identifies next steps.

@@

\cite{BockAlexander2018TITE}
\cite{KonovalovD2017RDfA}
\cite{Williams:2020:UIF}

>>>>

Since the digital collections may each contain tens of thousands of images, producing metadata for each image via a manual process is prohibitively labor-intensive and infeasible. Methods for automatically computing metadata from images are therefore needed to fully exploit biological image repositories for scientific discovery.
As a step towards improving metadata in specimen research image collections, members of the Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digital specimen.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which aims to develop a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of machine learning and image informatics tools and techniques, we can accurately determine general image quality and metadata such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
were  applied to a set of 7,247
images drawn from the Illinois Natural History Survey (INHS) Collection.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results are presented, followed by a discussion. The conclusion highlights key findings and identifies next steps.

@@

Bock 2018 \cite{BockAlexander2018TITE},
Konovalov 2017 \cite{KonovalovD2017RDfA},
Williams 2020 \cite{Williams:2020:UIF},
Hao 2015 \cite{Hao2015TheMO},
Lalabadi 2020 \cite{Lalabadi2020FishFC},
Wang 2015 \cite{Huihui2015StudyOT},
Saberioon 2017 \cite{Saberioon2017ApplicationOM},
Tappi 2017 \cite{Tappi2017ComputerVS},
Taheri-Garavand 2019 \cite{TaheriGaravand2019RealtimeNM},
Azarmdel 2019 \cite{Azarmdel2019DevelopingAO},
Bernardo 2020 \cite{Bernardo2020FishQI},
Konovalov 2018 \cite{Konovalov2018AutomaticSO},
Konovalov 2019 \cite{Konovalov2019AutomaticWE},
Lugatiman 2019 \cite{Lugatiman2019TunaMF},
Mu{\~n}oz-Benavent 2018 \cite{MuozBenavent2018EnhancedFB},
Petrov 2020 \cite{Petrov2020Overview},
G{\"u}m{\"u}ş 2011 \cite{Gm2011MachineVA},
Miranda 2017 \cite{MIRANDA201741},
Zion 2000 \cite{Zion2000InvivoFS},
Zion 2012 \cite{Zion2012ReviewTU}.
